\SECTION{Discussion}\label{sec:relatedwork}
Here, we discuss the comparing between proposed Linux-RTXG framework and previous work.

\begin{table*}[t]
\begin{center}
\caption{Linux-RTXG vs Prior Work}
\label{tab:comp:prior}
%\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|} \hline
\ifthesis
\scalebox{0.65}{
\fi
\begin{tabular}{ccccccccccc} \hline
 & CPU & CPU & GPU Prio. & Budget & Data/Comp. & Closed Src.& Kernel& OS & GPU Runtime \\ 
& FP & EDF & Sched. & Enforcement & Ovlp. & Compatible & Free & independent & independent \\ \hline
 RGEM       &   &   & x &   &   & x & x & x &   \\ 
 Gdev       &   &   & x & x & x &   &   &   &   \\ 
 PTask      &   &   & x & x & x & x &   &   & x \\ 
 GPUSync    & x & x & x & x & x & x &   &   & x \\ 
 GPUSparc   & ▲ &   & x &   & x & x &   & x &   \\ 
 Linux-RTXG & x & x & x & x & x & x & x & x & x \\ \hline
\end{tabular}
\ifthesis
}
\fi
\end{center}
\end{table*}

RGEM and GPU-Sparc~\cite{sparc} have GPU resource management without kernel and device driver modification.
However, the synchronization mechanisms of these methods depends on proprietary-software.
TimeGraph, Gdev, Ptask, and GPUSync realize independent synchronization mechanisms that do modify the kernel and device drivers.
To the best of our knowledge, the proposed Linux-RTXG is the only real-time GPU framework that uses a synchronization mechanisms
that are independent of runtime and do not modifiy the kernel and device drivers.

Table~\ref{tab:comp:prior} shows a comparison of the proposed Linux-RTXG and previous methods.
GPU sync supports the fixed-priority and EDF CPU scheduling policies.
GPUSparc employs the $SCHED\_FIFO$ Linux scheduling policies.
Note that Linux-RTXG demonstrates all features shown in Table~\ref{tab:comp:prior}.
In particular, Linux-RTXG is both GPU runtime independendt and OS independent.

More in-depth resource management would require detailed information about the execution mechanisms in black--box GPU stacks.
Menychtas et al. presented enabling to GPU using OS reserach by inferring interactions in a black--box GPU stack~\cite{menychtas2013enabling}.
We have presented information about GPU microcontrollers~\cite{fujii:apsys2013} and an open-source GPGPU runtime~\cite{kato:gdev}.
In addition, GPUSync verifies proprietary runtime chanism infomation.
The Nouveau project provide an open-source GPU driver~\cite{nouveau}.

The more-depth resource management would require the detail executing mechanisms in the black-box GPU stack.
Menychtas et al. present enabling GPU using OS research by inferring interaction in the black-box GPU stack~\cite{menychtas2013enabling}.
We present information of GPU microcontrollers~\cite{fujii:apsys2013} and an open-source GPGPU runtime~\cite{kato:gdev}.
GPUSync presents details verification information on the proprietary runtime mechanisms.
Nouveau project provides an open-source GPU driver~\cite{nouveau}.
%These works are very important, and we will also views of the further development of resource management their researches.

%In order to more growth the GPU as a powerful device,
%The challenges are efficiency compler, efficiency runtime, efficiency system such as treatment PCI.

%我々はこれまでいくつかのGPUの資源管理に関する研究~\cite{kato:timegraph,kato:rtas2011,kato:rgem,kato:gdev}を行ってきた。
%TimeGraphはGPUに送信されるコマンドをスケジューリングすることでCUDAにかぎらず、OpenGLなど、
%全てのGPUを利用に関する資源管理を行っている。
%しかしながらGPUのコマンドは処理の実行だけでなく、データ転送、割込み処理登録などの処理時にも送信されており、
%本当にスケジューリングするべき単位でのスケジューリングには向いていないことがわかっている。
%そのため、RGEMはGPGPUに特化し、GPUカーネル実行単位でのスケジューリングを目指し、固定優先度でのスケジューリングを実現してる。
%加えて、データ転送のセグメント分けによってノンプリエンプティブな特性にもたらされるデメリットを最小限にし、
%レスポンスタイムの向上を目指している。
%GdevはRGEMの発展形であり、仮想GPUとResource ReservationによるQoS制御や、OS空間でのCUDA実行などを実現している。
%加えてデータ転送とカーネル実行をオーバラップさせることで実行時間自体の縮小を実現している。
%
%PTask~\cite{ptask} is an OS abstraction for GPU applications that optimizes data transfers and GPU scheduler.
%
%Elliott et al. present GPUSync~\cite{elliott2013gpusync,elliott:explor14}.
%GPUSyncではホストからGPUへのデータ転送開始から、GPUでの処理、GPUからホストへのデータ転送までをクリティカルセクションと設定し、
%runtimeへのアクセスはクリティカルセクションを区切りとして単一のアクセスとなるように調停を行っている。
%これによってクローズドソースなランタイムを利用しつつ、自身のGPU資源管理を実現可能としている。
%GPUSyncはアクセス調停の手法としてk-exclusion lockの拡張を利用している。
%加えて各GPUごとにResource ReservationによるQoS担保を行っており、各GPU間のP2P migrationも実現しており、MultipleGPUへの自動割り当ても行っている。

%Han et al. show GPU-SPARC~\cite{sparc}.
%GPU-Sparc support to automatically split and run the GPU kernel concurrently over multi-GPU, and then they supported priority queue based scheduling.

